---
title: "Weight of Fish"
author: "Rabi Elkhoury"
date: "6/30/22"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fish <- read.csv(file  = "Fish.csv")
```

# Predicting Fish Weight


## Perch
```{r}
Perch <- filter(Fish, Species == "Perch")
Perch <- select(Perch, -Species)
```



### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Two regressor model
The best regressor model is the one with the Height and Weight variables as its two regressors.  The second best regression model is the one with Length3, Height, and Width as the regressors.


## Pike
```{r}
Pike <- filter(Fish, Species == "Pike")
Pike <- select(Pike, -Species)
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```




### Best Two regressor model
The best regressor model for the Pike data was evaluated to be the regression model with variables L1/L2/L3/H/W; data with these 5 regressors yielded nearly .980 for the adjusted r^2 value.  The second most accurate data came from the model with 4 regressors, with those four variables being L1/L3/H/W.

## Roach
```{r}
Roach <- filter(Fish, Species == "Roach")
Roach <- select(Roach, -Species)
```


### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Two regressor model
The most accurate regressor model, based on the statistics generated, is the one the 2 regressors length 3 and width, an adjusted r^2 value of nearly .9.  Second to that was the regression model with Width as the sole variable.
## Final Summary Statements
Adapting the automated regression model code, we were able to calulate models that best predicted the weight of different species of fish.  For the roach and perch fish, only head/width and length3/width were necessary to predict the fish weight.  However, for the pike fish, all 5 variables (L1, L2, L3, H, W) were required to produce an accurate modeling the species' weight.



