---
title: "Weight of Fish"
author: "Rabi Elkhoury"
date: "6/30/22"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fish <- read.csv(file  = "Fish.csv")
```

# Predicting Fish Weight


## Perch
```{r}
Perch <- filter(Fish, Species == "Perch")
Perch <- select(Perch, -Species)
```



### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Two regressor model
The best regressor model is the one with the Height and Weight variables as its two regressors.  The second best regression model is the one with Length3, Height, and Weight as the regressors.


## Pike
```{r}
Pike <- filter(Fish, Species == "Pike")
Pike <- select(Pike, -Species)
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```




### Best Two regressor model
The best regressor model for the Pike data was evaluated to be the regression model with variables L1/L2/L3/H/W; data with these 5 regressors yielded nearly .980 for the adjusted r^2 value.  The second most accurate data came from the model with 4 regressors, with those four variables being L1/L3/H/W.

## Roach




### Best Models

### Best Two regressor model

## Final Summary Statements